Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-10 cmsb22.tex
Answer two questions

  \sylvain{I'm not sure that \(e\) and \(s\) are very relevant, moreover they are not readily available\dots}

@@

\vangiang{Regarding the time differences, the reason might be that my implementation uses an ASP encoding based on choice rules instead of disjunctive rules or constraint rules.}
\sylvain{Maybe\dots I don't know ASP well enough to be sure. The fact that you go through a predicate \texttt{p} which adds one level of indirection might also have some effect, I'm not sure.}

>>>>

  \sylvain{I'm not sure that \(e\) and \(s\) are very relevant, moreover they are not readily available\dots}
  \vangiang{Indeed, they are not readily available. But if we use more meaningful words, the width of the table may exceed the width of the page. Thus, I use \(e\) and \(s\) along with the explanations shown in the table's caption. Do you have any other option?}

@@

\vangiang{Regarding the time differences, the reason might be that my implementation uses an ASP encoding based on choice rules instead of disjunctive rules or constraint rules.}
\sylvain{Maybe\dots I don't know ASP well enough to be sure. The fact that you go through a predicate \texttt{p} which adds one level of indirection might also have some effect, I'm not sure.}
\vangiang{Oh. I think that this may be a reason. However, I think we should still use a predicate \texttt{p(v, x)} in the paper because of the readability.}
